Probabilistic forecasting of hourly Emergency Department arrivals

### 2022-02-10 paper/paper.Rmd
address comments raised by Ivan

---
title:  Forecasting short-term hourly Emergency Department arrivals
author:
  - name: Bahmna Rostami Tabar
    email: rostami-tabarb@cardiff.ac.uk
    affiliation: Cardiff Business School
    footnote: 12
  - name: Jethro Browell
    email: jethro.browell@glasgow.ac.uk
    affiliation: University of Glasgow
    footnote: 1
  - name: Ivan Svetunkov
    email: i.svetunkov@lancaster.ac.uk
    affiliation: Lancaster University
    footnote: 1
address:
  - code: Cardiff Business School
    address: Cardiff Business School, Cardiff University, UK
  - code: University of Glasgow
    address: School of Mathematics and Statistics, University of Glasgow, UK
  - code: Lancaster University
    address: Centre for Marketing Analytics and Forecasting, Lancaster University, UK
footnote:
  - code: 12
    text: "Corresponding Author"
  - code: 1
    text: "Equal contribution"

@@

Furthermore, we consider an extnsion to the additive models for $\lambdat_t$ and $\mu_t$ above to incorporate school and public holidays into $D$. These models are labelled Poisson-2 and NOtr-2. We also performed experiments with the truncated $t$ distribution (Ttr-2) and negative binomial distribution (NBI-2), but these did not results in forecasts as well calibrated as the truncated normal.

@@

```{r tab-results, out.width= "50%", cache=FALSE}
results_table <- read_rds("results_table.rds")
knitr::kable(results_table, booktabs = T, 
             linesep = "",caption = "Summary of studies in hourly emergency care forecasting") %>% kableExtra::kable_styling(latex_options = c("hold_position"), font_size =11)
```

Evaluation metrics from the test period are presented in Table \@ref(tab:tab-results). They are ordered by Quantile Bias. The five models identified above have a Quantile Bias of 0.014 or less, which is substantially lower than the next group of forecasts with Quantile Biases of 0.037 and above, ETS being the only exception with a value of 0.019.

```{r Skill-rel2bench-reduced, fig.cap= "Pinball skill score for the seven best performing approaches.", fig.align='center',out.width= "70%"}
```

 Figure \@ref(fig:Skill-rel2bench-reduced) illustrates the trade-off between calibration and pinball skill. <!-- We may need to expand this-->

@@

@@

```{r time-accuracy, fig.cap= "Running time vs. forecast accuracy", fig.align='center',out.width= "70%"}
```

Finally, Figure \@ref(fig:time-accuracy) reports the forecast accuracy of each approach versus the computational time required to generate the forecast for a given forecasting horizon of 48 hours.
<!-- We need to explain this once we have th result for RMSE -->
<!-- ``` -->

>>>>

---
title:  Probabilistic forecasting of hourly Emergency Department arrivals
author:
  - name: Bahmna Rostami Tabar
    email: rostami-tabarb@cardiff.ac.uk
    affiliation: Cardiff Business School
    footnote: 12
  - name: Jethro Browell
    email: jethro.browell@glasgow.ac.uk
    affiliation: University of Glasgow
    footnote: 1
  - name: Ivan Svetunkov
    email: i.svetunkov@lancaster.ac.uk
    affiliation: Lancaster University
    footnote: 1
address:
  - code: Cardiff Business School
    address: Cardiff Business School, Cardiff University, UK
  - code: University of Glasgow
    address: School of Mathematics and Statistics, University of Glasgow, UK
  - code: Lancaster University
    address: Centre for Marketing Analytics and Forecasting, Lancaster University, UK
footnote:
  - code: 12
    text: "Corresponding Author"
  - code: 1
    text: "Equal contribution"

@@

Furthermore, we consider an extnsion to the additive models for $\lambda_t$ and $\mu_t$ above to incorporate school and public holidays into $D$. These models are labelled Poisson-2 and NOtr-2. We also performed experiments with the truncated $t$ distribution (Ttr-2) and negative binomial distribution (NBI-2), but these did not results in forecasts as well calibrated as the truncated normal.

@@

```{r Skill-rel2bench, fig.cap= "Pinball skill score for the seven best performing approaches.", fig.align='center',out.width= "100%"}
```

 Figure \@ref(fig:Skill-rel2bench) illustrates the trade-off between calibration and pinball skill. <!-- We may need to expand this-->

@@

```{r tab-results, out.width= "50%", cache=FALSE}
results_table <- read_rds("results_table.rds") %>% arrange(`Quantile Bias`)
results_table <- results_table %>% 
  mutate(Method = 
           case_when(Method == "tbats" ~ "TBATS",
                     Method == "prophet" ~ "Prophet",
                     TRUE ~ Method))
knitr::kable(results_table, booktabs = T, 
             linesep = "",caption = "Summary of studies in hourly emergency care forecasting") %>% kableExtra::kable_styling(latex_options = c("hold_position"), font_size =9)
```

In above figures, we only present the performance of the top seven methods. However, we have evaluated the performance of 14 methods. Evaluation metrics for all methods from the test period are presented in Table \@ref(tab:tab-results). They are ordered by Quantile Bias. The five models identified above have a Quantile Bias of 0.014 or less, which is substantially lower than the next group of forecasts with Quantile Biases of 0.037 and above, ETS being the only exception with a value of 0.019.

@@

```{r time-accuracy, fig.cap= "Speed (Running time) vs. forecast accuracy", fig.align='center',out.width="70%"}
```

Finally, Figure \@ref(fig:time-accuracy) reports the forecast accuracy of each approach presented in Table \@ref(tab:tab-results) versus the computational time required to generate the forecast for a given forecasting horizon of 48 hours. The x-axis represents the speed of each method as slow, moderate or fast.
<!-- We need to explain this once we have th result for RMSE -->
<!-- ``` -->
